Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-09-14 LaTeX/Turnover.tex
resolving conflict

We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection; a result that is not found with loose sex-linkage. 

@@

\noindent
where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
The diploid selection term, $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix).

>>>>

We find that tightly sex-linked genetic variation can favour the spread of new sex-determination systems in which the heterogametic sex changes (XY to ZW or ZW to XY) and the new sex-determining region is less closely linked (or unlinked) to the sex-linked locus under selection, which would not be predicted by previous theory. 

@@

\noindent
where $V_{A}=\bar{p}(1-\bar{p})$ is the variance in the frequency of $A$ and $S_{A}=(D^\male +\alpha_{\Delta}^\male+t^\male) - (D^\female+\alpha_{\Delta}^\female+t^\female)$ describes sex differences in selection for the $A$ versus $a$ across diploid selection, meiosis, and gametic competition.
The diploid selection term, $D^\Hermaphrodite=\big{(} \bar{p}s^\Hermaphrodite+(1-\bar{p})h^\Hermaphrodite s^\Hermaphrodite\big{)} -\big{(} \bar{p}h^\Hermaphrodite s^\Hermaphrodite+(1-\bar{p}) \big{)}$, is the difference in fitness between $A$ and $a$ alleles in diploids of sex $\Hermaphrodite \in \{\female,\male\}$, where $\bar{p}$ is the leading-order probability of mating with an $A$-bearing gamete from the opposite sex (see Appendix). The difference in $A$-allele-frequency among Y-bearing sperm versus X-bearing sperm is given by $\hat{p}^\male_Y-\hat{p}^\male_X=V_{A}\big{(}D^\male - D^\female+\alpha_{\Delta}^\male-\alpha_{\Delta}^\female+t^\male-t^\female\big{)}(1-2r)/2r$.
